Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-01-21 paper.tex
Minor Query R13: the two peaks of what?

The value of $k$ for each perturbation is calculated as $k
= 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
perturbation, measured as the difference between the two peaks closest to $z=0$
(thus minimising the influence of line-tying on the measurement). This gives
a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both
viscosity models. Hence, the observed most unstable fluting perturbation is
that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the
observed kink instability is that where $m=1$ and $k=4.57$. Using these values,
it is observed that the fluting perturbation exactly resonates with the field,
that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$
(Figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
of peak linear \rev{flute growth $r_s$} seen in
Figure~\ref{fig:growth_rate_4}. At this time the perturbation is close
to resonance, that is $m B_{\theta}(r)/r + kB_z(r)\approx 0$, over a
range of radii from $r=0.125$ to $0.2$.

>>>>

The value of $k$ for each \rev{instability mode} is calculated as $k
= 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
perturbation, measured as the difference between the two peaks closest to $z=0$
(thus minimising the influence of line-tying on the
measurement). \rev{In particular, the two peaks closest to $z=0$ of
  the pressure profile are used to calculate the wavenumber of
  the flute mode $k_{\text{flute}}$ and those of the radial velocity
  profile are used to calculate the wavenumber of
  the kink mode $k_{\text{kink}}$, respectively.} This gives
a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both
viscosity models. Hence, the observed most unstable fluting perturbation is
that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the
observed kink instability is that where $m=1$ and $k=4.57$. Using these values,
it is observed that the fluting perturbation exactly resonates with the field,
that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$
(Figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
of peak linear \rev{flute growth $r_s$} seen in
Figure~\ref{fig:growth_rate_4}. At this time the perturbation is close
to resonance, that is $m B_{\theta}(r)/r + kB_z(r)\approx 0$, over a
range of radii from $r=0.125$ to $0.2$.
